### 2015-04-13 src/misc/s2_discussion.tex
Updated discussion and added references

Navigating through the environment evokes complex changes of visual, auditory, vestibular, tactile and
motor inputs to the brain. Yet, despite this motion, we perceive the world as a stable reality, maintain an integrated sense of where we are, how we are oriented, and are able to track and act rather effortlessly upon surrounding objects.  How the ability comes about it one of the key questions in neuroscience and also studied in this research project. The objective was to build computational models and perform thorough psychometric testing in order to examine the physical and biological contrast that are placed on the interaction between the vestibular and other sensory systems for spatial orientation and self-motion perception. This resulted in the following contributions to the field:

>>>>

Navigating through the environment evokes complex changes of visual, auditory, vestibular, tactile and
motor inputs to the brain. Yet, despite these motion induced changes of input, we perceive the world as a stable reality, maintain an integrated sense of where we are, how we are oriented, and are able to track and act rather effortlessly upon surrounding objects. How this ability comes about is also the topic of this thesis. The object of the research project described in this thesis was to build computational models and perform thorough psychometric testing in order to unravel the physical and biological constraints on the interaction between the vestibular and other sensory systems for spatial orientation and self-motion perception. This resulted in the following contributions to the field:
